---
title: "Inference, visualization and analysis of neural-specific communication network"
author: TigerZ
date: 2023-4-25
output: 
  html_notebook: 
    toc: yes
    number_sections: yes
---

# Load NeuronChat library

```{r}
library(NeuronChat)
library(CellChat)
```



# Part I: Create NeuronChat object

```{r}
# 导入示例数据：Yao 2021 皮层数据, 已处理
data(list='cortex_data')
# 通过选择 VISp 区域来对数据进行取子集。
region_name <- 'VISp'
cell_class <- names(table(meta$class_label))
cell_idx <- which(meta$region_label %in% region_name & meta$class_label %in% cell_class & !(meta$subclass_label %in%c('Car3','CR','DG','L2/3 IT PPP','L5/6 IT TPE-ENT')))
target_df_single  <- target_df[cell_idx,] # 一个数据框：行是细胞，列是基因（最后一列是 cell subclass）。
meta_tmp <- meta[cell_idx,]
rownames(meta_tmp) <- meta_tmp$sample_name # subset meta
df_group <- meta_tmp[!duplicated(meta_tmp$subclass_label),c('class_label','subclass_label')]
group <- structure(df_group$class_label,names=df_group$subclass_label) # 为 subclasses 创建细胞类，用于绘图。

# 创建 NeuronChat 对象；选择“mouse”数据库用于小鼠数据；选择“human”用于人类数据。
# 请注意，第一个参数应该是一个数字矩阵，行是基因，列是细胞。
# createNeuronChat()从一个数据矩阵创建一个NeuronChat对象
x <- createNeuronChat(t(as.matrix(target_df_single[,1:(dim(target_df_single)[2]-1)])),DB='mouse',group.by = target_df_single$cell_subclass)
```



# Part II: Run NeuronChat to infer the neural-specific cell-cell communication networks

```{r}
# M用于permutation test；通常当M=100时大约需要4分钟，具体取决于数据集大小和细胞组数量。
# 可以设置 M=10 来更快地运行
x <- run_NeuronChat(x, M=10)
# 单个交互对的通信网络存储在“net”插槽中
# 将所有交互对的通信网络聚合，方法可以是“weight”、“count”等。
net_aggregated_x <- net_aggregation(x@net,method = 'weight')
```



# Part III: Visualization of neural-specific cell-cell communication networks

## for aggregated network

```{r fig.height=2, fig.width=4, message=FALSE, warning=FALSE}
par(mfrow=c(1,2))
# Visualization, circle plot, for the aggregated network
netVisual_circle_neuron(net_aggregated_x,group=group,vertex.label.cex = 1)
# Visualization, chordDiagram, for the aggregated network; also using cellchat function netVisual_chord_cell_internal(net_aggregated_x, group = group,lab.cex=1)
netVisual_chord_neuron(x,method = 'weight',group=group,lab.cex = 1)
```

```{r}
# Visualization, heatmap for the aggregated network
heatmap_aggregated(x, method='weight',group=group)
```

## for individual network

```{r fig.height=2, fig.width=4}
par(mfrow=c(1,2))
# Visualization for the single interaction pair, circle plot  
netVisual_circle_neuron(x@net$Glu_Gria2,group=group,vertex.label.cex = 1)
# Visualization for the single interaction pair, chord diagram 
netVisual_chord_neuron(x,interaction_use='Glu_Gria2',group=group,lab.cex = 1)
```

```{r fig.height=2, fig.width=3}
# Visualization for the single interaction pair, heatmap 
heatmap_single(x,interaction_name='Glu_Gria2',group=group)
```

```{r fig.height=2, fig.width=8}
# 用于单个交互对的可视化，热图与小提琴图显示与配体和靶标相关的基因表达。
lig_tar_heatmap(x,interaction_name='Glu_Gria2',width.vector=c(0.38,0.35,0.27))
```

# Part IV: Analysis of communication

## barplot 显示所有交互对的链接或信息流。

```{r fig.height=4, fig.width=2}
g1 <- rankNet_Neuron(x,slot.name = "net",measure = c("weight"),mode='single',font.size = 5) 
g2 <- rankNet_Neuron(x,slot.name = "net",measure = c("count"),mode='single',font.size = 5)
g1+g2
```

## outgoing/incoming pattern

```{r fig.height=2, fig.width=2, message=FALSE, warning=FALSE}
# selectK_Neuron(x,pattern = "outgoing")
# selectK_Neuron(x,pattern = "incoming")
x<- identifyCommunicationPatterns_Neuron(x, slot.name = "net", pattern = c("outgoing"), k=4,height = 18)
x<- identifyCommunicationPatterns_Neuron(x, slot.name = "net", pattern = c("incoming"), k=4,height = 18)
```

```{r warning=FALSE}
library(ggalluvial)
netAnalysis_river_Neuron(x,slot.name = "net", pattern = c("outgoing"),font.size = 2.5,cutoff.1 = 0.5,cutoff.2=0.5)
#> Please make sure you have load `library(ggalluvial)` when running this function
```

```{r}
netAnalysis_river_Neuron(x,slot.name = "net", pattern = c("incoming"),font.size = 2.5,cutoff.1 = 0.5,cutoff.2=0.5)
#> Please make sure you have load `library(ggalluvial)` when running this function
```



# manifold learning and classification

```{r warning=FALSE}
x <- computeNetSimilarity_Neuron(x,type='functional')
x  <- CellChat::netEmbedding(x, slot.name = "net_analysis", type = "functional")
#> Manifold learning of the signaling networks for a single dataset
x <- CellChat::netClustering(x, type='functional',slot.name = "net_analysis",k=5)
#> Classification learning of the signaling networks for a single dataset
netVisual_embedding_Neuron(x, type = "functional", label.size = 5,pathway.remove.show = F)
```

```{r}
netVisual_embeddingZoomIn_Neuron(x, type = "functional", nCol = 2,label.size = 3)
```














